Digital History in Finland, 1488-1828

### 2016-06-21 inst/examples/manuscript-krakow.Rmd
citations

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Handle citations
require(knitcitations)
cleanbib()
#options("citation_format" = "pandoc")
bib <- read.bibtex("bibliography.bib")
#opts_chunk$set(fig.width=4, fig.height=3, par=TRUE, out.width='2in', fig.pos='H')
#knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/", dev="CairoPNG")
knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/")
```

@@

@@

```{r, echo=FALSE, message=FALSE, results='asis'}
bibliography()
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Handle citations
require(knitcitations)
cleanbib()
#options("citation_format" = "pandoc")
cite_options(hyperlink = TRUE, max.names = 3)
bib <- read.bibtex("bibliography.bib")
#opts_chunk$set(fig.width=4, fig.height=3, par=TRUE, out.width='2in', fig.pos='H')
#knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/", dev="CairoPNG")
knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/")
```

@@

Embed citations from bib files with `r citep(bib[["lahti14natcomm"]])`.

@@

```{r, echo=FALSE, message=FALSE, results='asis'}
bibliography(sorting = 'ynt')
```
